---
title: "Assignment 4"
date: "January 10, 2023"
output: html_document
---

```{r setup, include=FALSE} 
# Set global chunk options
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE) 

# Add libraries
library("httr")
library("tidyverse")
library("DBI")
library("RSQLite")
library("RSelenium")
library("xml2")
library("rvest")
library("sf")
library("rnaturalearth")
library("tmap")
```

```{r}
#=========================================================
# Get Functions
#=========================================================
get_data <- function(url){
  
  # Use GET function to retrieve data from the specified URL
  data <- GET(url)
  
  # Parse the retrieved data
  data_parsed <- content(data, "parsed")
  
  # Return the parsed data
  return(data_parsed)
}

get_written_data <- function(base_url, skip_records, take_records){
  url <- paste0(base_url, skip_records, take_records) #construct first request
  
  written_data <- get_data(url) #get first request
  
  written_list <- list() #create a new list
  
  written_list <- append(written_list, written_data$results) #append first request to the list
  
  num_requests <- ceiling(written_data$totalResults / 100) #calculate number of requests needed
  
  for (i in 1:num_requests){ #for each request in num_requests
    
    cat("Getting request ", i, " out of ", num_requests, "\n") #update user
    
    skip_records <- skip_records + 100 #update the skip number
    
    url <- paste0(base_url, skip_records, take_records) #update the url
    
    written_data <- get_data(url) #get current request
    
    written_list <- append(written_list, written_data$results) #append current request to the list
    
    #add a pause
    Sys.sleep(2)
  }
  
  results <- map_df(written_list, create_written_df_row) #construct df with needed data
  
  return(results)
}

get_oral_data <- function(base_url, skip_records, take_records){
  url <- paste0(base_url, skip_records, take_records) #construct first request
  
  oral_data <- get_data(url) #get first request
  
  oral_list <- list() #create a new list
  
  oral_list <- append(oral_list, oral_data$Response) #append first request to the list

  num_requests <- ceiling(oral_data$PagingInfo$GlobalTotal / 100) #calculate number of requests needed
  
  for (i in 1:num_requests){ #for each request in num_requests
    
    cat("Getting request ", i, " out of ", num_requests, "\n") #update user
    
    skip_records <- skip_records + 100 #update the skip number
    
    url <- paste0(base_url, skip_records, take_records) #update the url
    
    oral_data <- get_data(url) #get current request
    
    oral_list <- append(oral_list, oral_data$Response) #append current request to the list
    
    #add a pause
    Sys.sleep(2)
  }
  
  results <- map_df(oral_list, create_oral_df_row) #construct df with needed data
  
  return(results)
}

get_geo_ids <- function(url, selector_list, df){
  # Create driver
  rD <- rsDriver(browser=c("firefox"), verbose = F, 
                   port = netstat::free_port(random = TRUE), 
                   chromever = NULL) 
  
  driver <- rD$client
  
  #Create list to store geo data
  geography_ids <- list()
  
  # Loop through constituencies
  for (curr_constituency in df$constituency){
    cat("Getting data for ", curr_constituency, "\n")
    
    #navigate to homepage
    driver$navigate(url)
    
    #wait for page to load
    Sys.sleep(2)
    
    tryCatch(
          {
            #try to find the search bar
            search_box <- driver$findElement(using = "xpath",
                                             value = selector_list$search_box)
          },
          error = function(e){ #if the search bar isn't found
            cat("Trying ", constituency, " again\n")
            
            # Add a pause
            Sys.sleep(2)
            
            # Try to find the search bar again
            search_box <- driver$findElement(using = "xpath",
                                             value = selector_list$search_box)
            
          }
        )
    
    # Send the constituency name into the search bar
    search_box$sendKeysToElement(list(curr_constituency))
    
    # Wait for options to pop up
    Sys.sleep(2)
    
    # Set flag to indicate whether the appropriate option was found
    element_found <- FALSE
  
    while (!element_found) { #while the element has not been found
      
      tryCatch(
        {
          # Search for parliamentary constituency we are collecting data for
          option <- driver$findElement("xpath", 
                                       paste0("//div[contains(@class, 'listItem')",
                                       " and contains(., 'Parliamentary constituency')]"))
          
          # If the element is found, set the flag to exit the loop
          element_found <- TRUE
        },
        error = function(e) { # If the element is not found
          cat("Trying ", curr_constituency, " again\n")
          
          # Add a pause
          Sys.sleep(2)
          
          # Try to find the option again
          option <- driver$findElement("xpath", 
                                       paste0("//div[contains(@class, 'listItem')",
                                       " and contains(., 'Parliamentary constituency')]"))
        }
      )
    }
    
    # Click that parliamentary constituency
    option$clickElement()
    
    # Wait for the page to load
    Sys.sleep(2)
    
    #Get the string that has the geographic ID in it
    geo_id <- driver$findElement("xpath", 
                                 '//*[@id="main"]/div[2]/div/p')$getElementText()
    
    # Add the string to the list
    geography_ids <- c(geography_ids, geo_id)
  }
  
  # Close the driver
  driver$close()
  
  # Return the geo ids
  return(geography_ids)
}

get_region <- function(link_texts) {
  
  # Iterate through each link_text in the provided vector
  for (link_text in link_texts) {
    
    # Check if "England" is present in the current link_text
    if ("England" %in% link_text) {
      return("England")  # Return "England" if found
    } 
    # Check if "Scotland" is present in the current link_text
    else if ("Scotland" %in% link_text) {
      return("Scotland")  # Return "Scotland" if found
    } 
    # Check if "Northern Ireland" is present in the current link_text
    else if ("Northern Ireland" %in% link_text) {
      return("Northern Ireland")  # Return "Northern Ireland" if found
    } 
    # Check if "Wales" is present in the current link_text
    else if ("Wales" %in% link_text) {
      return("Wales")  # Return "Wales" if found
    }
  }
  
  # If none of the regions are found, return NA
  return(NA)
}

get_regions <- function(df){
  
  # Define the base URL for constructing complete URLs
  base_url <- 'https://www.ons.gov.uk/visualisations/areas/'
  
  # Initialize an empty vector to store the regions
  regions <- c()
  
  # Iterate through each constituency_id in the geo_ids column of the df
  for (constituency_id in df$geo_ids){
    
    # Print a message indicating the data retrieval process
    cat("Getting data for ", constituency_id, "\n")
    
    # Construct the complete URL
    url <- paste0(base_url, constituency_id, "/")
    
    # Read the HTML content from the constructed URL
    html_content <- read_html(url)
    
    # Extract all link texts from the HTML content using the get_all_links function
    link_data <- get_all_links(html_content)
  
    # Extract the link_texts component from the link_data
    link_data$link_texts
    
    # Use the get_region function to identify the region based on link_texts
    region <- get_region(link_data$link_texts)
    
    # Append the identified region to the regions vector
    regions <- c(regions, region)
  }
  
  # Return the vector containing the identified regions for each constituency
  return(regions)
}

get_all_links <- function(html){ # Gets all links from the input HTML
  
  # Extract all hyperlink elements from the provided HTML
  link_elements <- html %>% 
    html_elements(css = "a")
  
  # Extract the text content from the extracted urls.
  link_texts <- link_elements %>% html_text()
  
  # Create a list containing the elements and their corresponding texts
  link_data <- list("link_elements" = link_elements, 
                    "link_texts" = link_texts)
  
  # Return the created list containing link_elements and link_texts.
  return(link_data)
}

#=========================================================
# Create Functions
#=========================================================
create_written_df_row <- function(element){
  
  # Create a new row using the tibble function with specified column values
  new_row <- tibble(
    asking_member_id = element$value$askingMemberId,  
    asking_member_name = element$value$askingMember$name,
    asking_member_party = element$value$askingMember$party,
    asking_member_from = element$value$askingMember$memberFrom,
    answering_body_name = element$value$answeringBodyName
  )
  
  # Return the newly created row as a tibble
  return(new_row)
}

create_oral_df_row <- function(element){
  
  # Create a new row using the tibble function with specified column values
  new_row <- tibble(
    asking_member_id = element$AskingMemberId,  
    asking_member_name = element$AskingMember$Name,
    asking_member_party = element$AskingMember$Party,
    asking_member_from = element$AskingMember$Constituency,
    answering_body_name = element$AnsweringBody
  )
  
  # Return the newly created row as a tibble
  return(new_row)
}

#=========================================================
# Processing Functions
#=========================================================
process_questions <- function(df){
  # Group the combined data by asking_member_id 
  df_grouped <- df %>%
    group_by(asking_member_id) %>%
  
    # Summarize the data: calculate counts and majority-related columns
    summarise(
      health_welfare_count = sum(answering_body_name %in% c("Department of Health and Social Care", 
                                                            "Department for Work and Pensions")),
      
      economic_count = sum(!answering_body_name %in% c("Department of Health and Social Care", 
                                                       "Department for Work and Pensions")),
      
      health_welfare_proportion = round(health_welfare_count/ (health_welfare_count + 
                                                                 economic_count), 
                                        2),
      
      economic_proportion = 1- health_welfare_proportion)

  # Left join the grouped data with additional information from the original df
  df_processed <- left_join(df_grouped, df %>%
                                         
                         # Keep only distinct records based on asking_member_id
                         distinct(asking_member_id, .keep_all = TRUE), 
                         
                         by = "asking_member_id") %>%
    
    # Select specific columns for the final processed dataframe
    select(c(asking_member_name, 
             asking_member_party, 
             asking_member_from, 
             health_welfare_proportion, 
             economic_proportion)) %>%
    
    rename(constituency = asking_member_from)
  
  return (df_processed)
}

#=========================================================
# Cleaning Functions
#=========================================================
clean_geo_id <- function(input_string) {
  # Extract text within parentheses
  geo_id_processed <- regmatches(input_string,
                                 regexpr("\\(([^)]+)\\)",
                                         input_string))
  
  # Remove parentheses
  geo_clean <- gsub("[()]", "", geo_id_processed)
  
  # Return the cleaned result
  return(geo_clean)
}
```

```{r}
# Set the path to the SQLite database
database = 'database/parliament_data.db'
```

```{r eval=FALSE}
#=========================================================
# Get Written Question Data
#=========================================================

# Set the base URL for the written questions API with specific parameters
written_base_url <- paste0('https://questions-statements-api.parliament.uk/',
                           'api/writtenquestions/questions?', 
                           'tabledWhenFrom=2021-01-01&tabledWhenTo=2022-12-31',
                           '&includeWithdrawn=true&expandMember=true',
                           '&answeringBodies=17&answeringBodies=14&answeringBodies=214',
                           '&answeringBodies=202&answeringBodies=29',
                           '&house=Commons&skip=')

# Set the number of records to skip for pagination
written_skip_records <- 0

# Set the number of records to take per request
written_take_records <- '&take=100'

# Retrieve data using the written questions API
written_df <- get_written_data(written_base_url,
                               written_skip_records,
                               written_take_records)

#=========================================================
# Get Oral Question Data
#=========================================================

# Set the base URL for the oral questions API with specific parameters
oral_base_url <- paste0('https://oralquestionsandmotions-api.parliament.uk',
                        '/oralquestions/list?',
                        'parameters.answeringDateStart=2021-01-01',
                        '&parameters.answeringDateEnd=2022-12-31',
                        '&parameters.answeringBodyIds=17&parameters.answeringBodyIds=14',
                        '&parameters.answeringBodyIds=214&parameters.answeringBodyIds=202',
                        '&parameters.answeringBodyIds=29&parameters.skip=')

# Set the number of records to skip for pagination
oral_skip_records <- 0

# Set the number of records to take per request
oral_take_records <- '&parameters.take=100'

# Retrieve data using the oral questions API
oral_df <- get_oral_data(oral_base_url,
                         oral_skip_records,
                         oral_take_records)

#=========================================================
# Process Question Data
#=========================================================

# Combine written and oral question data 
all_questions_df <- rbind(written_df, oral_df)

all_questions_processed <- process_questions(all_questions_df)

# Remove questions from Members who were removed from office mid-year
values_to_remove <- c("Neil Parish", "Kate Green", "Sir David Amess",
                      "Mr Owen Paterson", "Jack Dromey", "Neil Gray",
                      "Tracy Brabin", "Mike Hill", "Imran Ahmad Khan")

# Remove values
questions_filtered <- all_questions_processed[
  !all_questions_processed$asking_member_name %in% values_to_remove, ]

# Connect to the SQLite database
db <- dbConnect(RSQLite::SQLite(), database)

# Write the processed data into the database
dbWriteTable(db, "member_details", questions_filtered)

# Disconnect from the database
dbDisconnect(db)

```

### Introduction

In the realm of parliamentary scrutiny, where oral and written questions empower Members of Parliament (MPs) to delve into governmental actions and policies, this investigation seeks to unravel the dynamics shaping their interrogations. Two key questions guide this exploration:

- Does party affiliation influence the focus of MPs' questions in the House of Commons? 
  + This research focuses on written and oral inquiries pertaining to health and welfare versus economic matters tabled and answered from 2021-2022.

- To what degree do variations in MPs' rates of posing questions about health and welfare versus economic issues mirror regional disparities in their constituencies' broader health and economic landscapes? 
  + This inquiry delves into whether party affiliation remains the predominant force steering MPs' questioning patterns or if Members of Parliament reveal a nuanced responsiveness to the unique needs of their constituents. Essentially, we scrutinize whether questioning behavior aligns more with party conventions or genuinely reflects the urgent concerns of the communities they represent.


### Data

I collected data from the [UK Parliament API](https://developer.parliament.uk/), encompassing 36,452 written and oral questions posed by 554 Members of Parliament between January 2021 and December 2022. To discern the nature of these questions—whether they pertained to health and welfare or economic matters—I selectively included questions answered by specific Answering Bodies. Economic questions were identified through responses from the Department for Business and Trade, Department for International Trade, and the Treasury. While the Department of Treasury is the primary entity for financial and economic policy, including the other two ensures a more comprehensive analysis of "economic issues," as they also support businesses in the UK.

Questions answered by the Department for Work and Pensions and the Department of Health and Social Care were categorized as health and welfare questions. The exclusion of other governmental bodies from the analysis is deliberate, as their primary focus is not on health, welfare, or economic issues. This strategic narrowing of scope mitigates the risk of over-including irrelevant questions in a text analysis based on keywords like "health," "welfare," or "economic."

Regional context was obtained from the (Office for National Statistics)[https://www.ons.gov.uk/], aligning constituencies with regions. The analysis aims to explore if constituencies with lower health levels align with health-welfare-focused parties and if higher economic activity aligns with parties addressing economic issues.

I excluded questions from MPs representing Scottish and Irish constituencies due to limited data on the general health and economic activity of these areas. 9 members were removed who left office mid-year so this analysis only includes the most recent members in office.

Table 1 shows the number of Labour and Conservative party members we collected data on during the 2021-2022 period.

```{r, echo = TRUE}
db <- dbConnect(RSQLite::SQLite(), database)

data <- dbGetQuery(db,
           "SELECT * 
           FROM member_details")

dbDisconnect(db)

show_data <- data %>%
  group_by(asking_member_party) %>%  
  summarise(
    Count = n()  
  ) %>%
  rename(Party = asking_member_party)

knitr::kable(show_data, caption = "Table 1: Number of members in each party")
```


```{r, eval= FALSE}
#=========================================================
# Get Geo Data
#=========================================================

db <- dbConnect(RSQLite::SQLite(), database)

member_constituencies <- dbGetQuery(db,
           "SELECT asking_member_name, 
           constituency, 
           asking_member_party, 
           health_welfare_proportion, 
           economic_proportion 
           FROM member_details")

dbDisconnect(db)

# Define search box Xpath
search_box_path <- list('//*[@id="search"]')
names(search_box_path) <- "search_box"

# Define homepage url
url <- "https://www.ons.gov.uk/visualisations/areas/"

# Geo geography ids for each constituency
geography_ids <- get_geo_ids(url, search_box_path, member_constituencies)

# Apply the function to each element in the list
cleaned_geo_ids <- lapply(geography_ids, clean_geo_id)

# Add geo ids to member constituencies
member_constituencies$geo_ids <- unlist(cleaned_geo_ids)

# Add regions to member constituencies
member_constituencies$region <- get_regions(member_constituencies)

# Filter only to constituencies in England and Wales
member_constituencies_filtered <- member_constituencies %>%
  subset(region %in% c("England", "Wales"))

parties_clean <- member_constituencies_filtered %>%
  mutate(asking_member_party = ifelse(
    asking_member_party %in% c("Conservative", 
                               "Labour"),
    asking_member_party,
    "Other")) %>%
  select (-geo_ids)

# Connect to the SQLite database
db <- dbConnect(RSQLite::SQLite(), database)

# Write geo data into the database
dbWriteTable(db, "member_details", parties_clean, overwrite = TRUE)

# Disconnect from the database
dbDisconnect(db)

```

## Analysis

*Question #1 : Does party affiliation influence the focus of MPs' questions in the House of Commons?*

In the context of questions asked to these answering bodies, the answer is yes.

In questions to specific Answering Bodies, party affiliation does influence questioning focus. Figures 1 and 2 show Labour's higher median percentage (around 81%) of questions related to health and welfare, while Conservatives lead in economic issues with a median of 33%. Labour exhibits a narrower range, emphasizing a consistent focus on health and welfare. Conversely, Conservatives show a broader spectrum, reflecting varied questioning levels.

```{r, include=FALSE,results='hide',fig.keep='all'}
#=========================================================
# Box Plots
#=========================================================

# Connect to the SQLite database
db <- dbConnect(RSQLite::SQLite(), database)

boxplot_data <- dbGetQuery(db,
           "SELECT asking_member_party, 
           health_welfare_proportion, 
           economic_proportion 
           FROM member_details")

# Disconnect from the database
dbDisconnect(db)

ggplot(boxplot_data, aes(x = asking_member_party, y = health_welfare_proportion)) +
  geom_boxplot() +
  labs(title = "Figure 1 \n Percentage of Questions asked about Health and Welfare",
       x = "Asking Member Party", y = "Percentage") +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  scale_y_continuous(labels = function(x) paste0(sprintf("%.0f", x*100), "%")) +
  theme_minimal()

ggplot(boxplot_data, aes(x = asking_member_party, y = economic_proportion)) +
  geom_boxplot() +
  labs(title = "Figure 2 \n Percentage of Questions asked about Economic Topics",
       x = "Asking Member Party", y = "Percentage") +
  scale_y_continuous(labels = scales::percent_format(scale = 1)) +
  scale_y_continuous(labels = function(x) paste0(sprintf("%.0f", x*100), "%")) +
  theme_minimal()
  
```

```{r}
#=========================================================
# Create Maps
#=========================================================

# Connect to the SQLite database
db <- dbConnect(RSQLite::SQLite(), database)

map_data <- dbGetQuery(db,
           "SELECT constituency, 
           asking_member_party,
           region
           FROM member_details")

member_constituencies <- map_data %>%
  mutate(asking_member_from = ifelse(constituency == "Weston-super-Mare",
                                     "Weston-Super-Mare",
                                     constituency))

# Disconnect from the database
dbDisconnect(db)

general_health <- read_csv("data/RM044-2021-2-filtered-2023-12-29T15_14_29Z.csv")

economic_activity <- read_csv("data/TS066-2021-6-filtered-2024-01-05T11_06_34Z.csv")

general_health_processed <- general_health %>%
  group_by(`Westminster Parliamentary constituencies`) %>%
  summarise(
    good_health_proportion = sum(Observation[
      `General health (6 categories)` %in% 
        c("Very good health", 
          "Good health")]) /
      sum(Observation)
  ) %>%
  ungroup()

economic_processed <- economic_activity %>%
  group_by(`Westminster Parliamentary constituencies`) %>%
  summarise(
    economic_activity_proportion = sum(Observation[
      grepl("Economically active", `Economic activity status (20 categories)`)]) /
      sum(Observation)
  ) %>%
  ungroup()

health_data <- left_join(map_data,
                         general_health_processed,
                         by = c("constituency" = "Westminster Parliamentary constituencies"))

health_economic_data <- left_join(health_data,
                         economic_processed,
                         by = c("constituency" = "Westminster Parliamentary constituencies"))

```


```{r fig.width = 13, fig.height = 13}
england_wales <- st_as_sf(ne_countries(geounit = c("England", 
                                        "Wales"),
                            type = "map_units"))

constituencies_shp <- read_sf(paste0("data/",
                              "Westminster_Parliamentary_Constituencies_",
                              "Dec_2021_UK_BFE_2022_-7013535748659767197/",
                              "PCON_DEC_2021_UK_BFE.shp"))

constituencies_shp_merged <- constituencies_shp %>%
  left_join(health_economic_data, 
            by = join_by(PCON21NM == constituency)) %>%
  
  #remove rows that are not a aprt of our analysis
  filter(!is.na(region))

parties <- tm_shape(constituencies_shp_merged) +
  tm_borders(lwd=0.3) +
  tm_fill(col = "asking_member_party", palette = c("lightblue", "lightcoral", "grey80")) +
  tm_layout(title = "Figure 3 \n Constituency Map by Party") +
  # Highlight Wales with a thicker border
  tm_shape(constituencies_shp_merged[constituencies_shp_merged$region == "Wales", ]) +
  tm_borders(lwd=1)

health_map <- tm_shape(constituencies_shp_merged) +
  tm_borders() +
  tm_fill(
    col = "good_health_proportion",
    palette = "Greys",  # Choose a color palette
    style = "cont",
    alpha = 1
  ) +
  tm_layout(title = "Figure 4 \n Constituency Map by proportion of population in Good Health") +
  tm_shape(constituencies_shp_merged[constituencies_shp_merged$region == "Wales", ]) +
  tm_borders(lwd=1)

economic_map <- tm_shape(constituencies_shp_merged) +
  tm_borders() +
  tm_fill(
    col = "economic_activity_proportion",
    palette = "Greens",  # Choose a color palette
    style = "cont",
    alpha = 1
  ) +
  tm_layout(title = "Figure 5 \n Constituency Map by Economic Activity Level") +
  tm_shape(constituencies_shp_merged[constituencies_shp_merged$region == "Wales", ]) +
  tm_borders(lwd=1)

```

*Question #2 : To what degree do variations in MPs' rates of posing questions about health and welfare versus economic issues mirror regional disparities in their constituencies' broader health and economic landscapes?*

Figure 3 illustrates party representation across regions. Figures 4 and 5, depicting health and economic indicators, showing a concentration of higher economic activity and general health levels around greater London, indicating potential alignment. However, Tables 2 and 3 reveal similar health and economic levels for Conservative and Labour constituencies, suggesting that these indicators may not strongly correlate with MPs' questioning behavior. This raises questions about the true reflection of constituency needs in MPs' behavior and the influence of external pressures.

The analysis sheds light on the nuanced relationship between MPs' party affiliation, questioning behavior, and regional disparities. While party affiliation influences questioning focus, regional health and economic indicators may not be strong predictors. This prompts further exploration into the multifaceted factors shaping MPs' behavior and the complex interplay between party conventions and constituency needs. The findings highlight the need for a comprehensive understanding of parliamentary dynamics, considering both national party dynamics and local factors influencing MPs' representation of their constituents.

```{r}
parties

```

```{r}
tmap_arrange(health_map, economic_map, ncol = 2)

```


```{r}
summary_table_labour <- health_economic_data %>%
  filter(asking_member_party == "Labour") %>%  
  summarise(
    good_health_mean = mean(good_health_proportion),
    good_health_standard_deviation = sd(good_health_proportion),
    economic_activity_mean = mean(economic_activity_proportion),
    economic_activity_deviation = sd(economic_activity_proportion),
    Count = n()  
  )

# Summary table for Conservative party
summary_table_conservative <- health_economic_data %>%
  filter(asking_member_party == "Conservative") %>% 
  summarise(
    good_health_mean = mean(good_health_proportion, na.rm = TRUE),
    good_health_standard_deviation = sd(good_health_proportion, na.rm = TRUE),
    economic_activity_mean = mean(economic_activity_proportion, na.rm = TRUE),
    economic_activity_deviation = sd(economic_activity_proportion, na.rm = TRUE),
    Count = n()  
  )

knitr::kable(summary_table_labour, caption = "Table 2: Labour Party Summary Statistics")

knitr::kable(summary_table_conservative, caption = "Table 3: Conservative Party Summary Statistics")
```

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 
# this chunk generates the complete code appendix. 
# eval=FALSE tells R not to run (``evaluate'') the code here (it was already run before).
```
