---
title: "Assignment Template"
author: "Dr Thomas Robinson and Dr Dan de Kadt"
date: "AT 2023"
output: html_document
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = FALSE) # actually set the global chunk options. 
library("jsonlite")
library("tidyverse")
library("DBI")
library("RSQLite")
```

```{r}
#set the base url
#set the skip_records
#set_take_records

#perform the first request

#parse the data

#calculate the number of times we are going to need to make the request by using totalResults
#set this number as num_requests

#create a new list (new_list <- list())

#append the results to the new list ( new_list <- append(new_list, written_questions_parsed$results)) )

#for each request in num_requests
  #construct the request making sure to update the skip number
  #parse the data (written_questions_parsed <- content(written_questions_get, "parsed") #httr)

  #add it to the master list

  #print progress

  #add a pause

#construct the master df

#set question id
#set asking member id
#set asking member name (written_questions_parsed$results[[i]]$value$askingMember$name)
#set asking member party (written_questions_parsed$results[[i]]$value$askingMember$party)
#set asking member from (written_questions_parsed$results[[i]]$value$askingMember$memberFrom)
#set member has interest
#answeringBodyName


# for (i in seq_along(written_questions_parsed$results)){ print(written_questions_parsed$results[[i]]$value$askingMember$name)}

#store the data in a db

#gender
#where they are from
```


```{r}
get_qs <- function(endpoint_url, n_skip = 0) {
  url <- paste0(
    endpoint_url,
    "?parameters.skip=",
    n_skip,
    "&parameters.take=100")

  response <-
    GET(url) |>
    content("parsed")

  return(response)
}

pull_all_written_qs <- function(endpoint_url){

  # Calculate how many questions are in the end point
  n_resp <- GET(endpoint_url) |>
    content("parsed")
  n <- n_resp$totalResults


  # Questions can be pulled in batches of 100,
  # calculate how many time we will have to pull
  n_loops <- ceiling(n / 100)

  print(paste0("Written Qs started at ", Sys.time()))

  for (i in 1:n_loops) {

    n_skip <- (i - 1) * 100 # Skip however many 100s the loop has run

    if (i == 1) { # On first iteration, make new list

      response <- get_qs(endpoint_url, n_skip)
      response <- response$results

    } else { # On all other iterations, append to existing list

      response_new <- get_qs(endpoint_url, n_skip)
      response_new <- response_new$results
      response <- c(response, response_new) # Merge responses

    }

    print(paste0(i, " of ", n_loops, " done.")) # Print progress message
    Sys.sleep(1) # Sleep to avoid hammering the API 

  }

  print(paste0("Written Qs done at ", Sys.time()))
  return(response)
}

written_questions <- pull_all_written_qs(
  "https://questions-statements-api.parliament.uk/api/writtenquestions/questions?tabledWhenFrom=2022-01-01&tabledWhenTo=2022-01-10&answered=Any&questionStatus=AllQuestions&includeWithdrawn=true&expandMember=true&answeringBodies=17&answeringBodies=14&answeringBodies=214&answeringBodies=202&answeringBodies=29&house=Commons")

for (i in seq_along(written_questions)){
  print(written_questions[[i]]$value$askingMemberId)
}

written_questions[[i]]$value$askingMember

summary(written_questions[[6]]$value)
```

```{r}
written_questions_get <- GET('https://questions-statements-api.parliament.uk/api/writtenquestions/questions?tabledWhenFrom=2022-01-01&tabledWhenTo=2022-01-02&answered=Any&questionStatus=AllQuestions&includeWithdrawn=true&expandMember=true&answeringBodies=17&answeringBodies=14&answeringBodies=214&answeringBodies=202&answeringBodies=29&house=Commons')

written_questions_parsed <- content(written_questions_get, "parsed") #httr

for (i in seq_along(written_questions_parsed$results)){
  print(written_questions_parsed$results[[i]]$value$askingMember$name)
}
```



This document contains the necessary commands and layout to meet the formatting requirements for MY472. You should use the template.Rmd file as the basis for your own answers to the assigned exercises.

## Formatting requirements

* You must present all results in full sentences, as you would in a report or academic piece of writing
  
  * If the exercise requires generating a table or figure, you should include at least one sentence introducing and explaining it. E.g. "The table below reports the counts of Wikipedia articles mentioning the LSE, by type of article."

* Unless stated otherwise, all code used to answer the exercises should be included as a code appendix at the end of the script. This formatting can be achieved by following the guidance in this template file.

* All code should be annotated with comments, to help the marker understand what you have done

* Your output should be replicable. Any result/table/figure that cannot be traced back to your code will not be marked

## Example of in-line figures without code

For those interested, we achieve the formatting requirements in two-steps: 1) in the `setup` chunk, we set `knitr::opts_chunk$set(echo = FALSE)` so that code is not included (echoed) by default in code chunks; 2) we add a specific chunk at the end of the file to collect and print *all* the code in the Rmarkdown file. Do not delete the final code chunk from the template!

For example, below we use a code chunk to generate random data and include a scatter plot in-line. The code used to generate this chart is only reported at the end of the document. 

```{r plot_example}
set.seed(89) # set a seed for R's psuedo-randomiser, for replicability.
x <- rnorm(100) # randomly draw 100 obs from normal distribution, save as object
y <- rnorm(100) 
plot(x,y) # two-way scatterplot using R's default plotting
```

In specific instances, however, you may be directed to report your code in-line (or you may want to do this to illustrate a specific point). In these cases, we can override the default behaviour by adding the chunk option `echo = TRUE` to a specific R chunk. When `echo=TRUE`, your code is presented in-line with any output displayed afterwards. The same code will also be included in the appendix at the bottom of the document (which is fine).

```{r echo_example, echo=TRUE}
# {[language] [chunk_name], [chunk_options]}
# here we use echo=TRUE to override our global options and make the chunk appear exactly here. 

print("This code chunk is visible in this section.")
```

## Appendix: All code in this assignment

```{r ref.label=knitr::all_labels(), echo=TRUE, eval=FALSE} 
# this chunk generates the complete code appendix. 
# eval=FALSE tells R not to run (``evaluate'') the code here (it was already run before).
```
